A mechanical Model of Rod-Shaped Bacteria

### 2025-01-29 paper/main.tex
add subsection for comparing across cell-divisions

>>>>

% --------------------------------------------------------------------------------------------------
\subsection{Comparing Results Across Generations}

\begin{figure}
    \centering
    \begin{tikzonimage}[width=0.3\textwidth]
        {../docs/source/_static/fitting-methods/progressions-1.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{a}};
    \end{tikzonimage}
    \begin{tikzonimage}[width=0.3\textwidth]
        {../docs/source/_static/fitting-methods/progressions-2.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{b}};
    \end{tikzonimage}
    \linebreak
    \begin{tikzonimage}[width=0.3\textwidth]
        {../docs/source/_static/fitting-methods/progressions-3.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{c}};
    \end{tikzonimage}
    \begin{tikzonimage}[width=0.3\textwidth]
        {../docs/source/_static/fitting-methods/progressions-4.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{d}};
    \end{tikzonimage}
    \caption{TODO}
    \label{fig:mask-difference-metric}
\end{figure}
